\documentclass[12pt]{article}
\usepackage{../frankstyle}


\begin{document}
\section*{Typos}

I put how we should change after the arrow $\rightarrow$. 

\begin{itemize}
\item p.6 1st paragraph last sentence: concerning the triangular array Assumption 2.1. $\rightarrow$ triangular array in Assumption 2.1. 
\item p.6 right below Assumption 2.2.: $E[f(Z_i, \gamma_0, \theta_0))]=0$ $\rightarrow$ $E[f(Z_i, \gamma_0, \theta_0)] = 0$
\item p.7 footnote 2: Assumption 2.2. of ?. needs to be complete.
\item p.8 right before Theorem 2.1.: The key results is $\rightarrow$ result is
\item p.10 equation (13) $\phi_0'$ $\rightarrow$ $\varphi_0'$
\item p.10 footnote 3: see ? Section 3.3. needs to be complete.
\item p.14 section 5.1. first sentence: in which the the GFIC $\rightarrow$ in which the GFIC 
\item p.15 right after equation (22): $\iota\iota'$ $\rightarrow$ $\iota_T \iota_T'$
\item p.16 right after the expression for $\sigma^2$: unbiased estimator of $\tau$. Thus, substituting $\widehat{\tau}-\sigma^2$ for $\tau$ $\rightarrow$ unbiased estimator of $\tau^2$. Thus substituting $\widehat{\tau}^2-\sigma^2$ for $\tau^2$. 
\item p.16 with the expressions for variance estimators $\widehat{\sigma}_\epsilon^2$ and $\widehat{\sigma}_v^2$, we should change $N$ with $n$. 
\item p.16 last part: $\omega^{*} = [...]$ $\rightarrow$ $\omega^{*} = [...]^{-1}$. Also, the sentence right after this expression should be: where we take the maximum over $\widehat{\tau}^2 - \widehat{\sigma}^2$ and zero...
\item p.22 last part of section 5.2.: by sputting zero in place of $\rightarrow$ by putting zero in place of
\item p.38 in Proof of Corollary 3.5. $(N_g', N_h)'$ $\rightarrow$ $(N_g', N_h')'$
\item p.39 in Proof of Theorem 5.1. The expressions should be changed into parts written in red below:\\
Now expanding $\widehat{\beta}_{FE}, \textcolor{red}{\widehat{\beta}_{RE}},$ and $\widehat{\tau}$ and re-arranging
\[\begin{bmatrix}
\sqrt{n}(\widehat{\beta}_{RE} - \beta)\\
\sqrt{n}(\widehat{\beta}_{FE}-\beta)\\
\widehat{\tau}
\end{bmatrix} =\begin{bmatrix}
A_n^{-1} & 0\\
0 & B_n^{-1} \\
C_n & -C_n \textcolor{red}{A_n}B_n^{-1}
\end{bmatrix}\begin{bmatrix}
n^{-1/2}\sum_{i=1}^n \mathbf{x}_i' \textcolor{red}{\widehat{\Omega}^{-1}} \mathbf{v}_i\\
n^{-1/2}\sum_{i=1}^n \mathbf{x}_i'Q \mathbf{v}_i
\end{bmatrix} 
\]
\end{itemize}

\newpage
\textcolor{red}{*** So far, the sections I've checked: Intro, 2, 3, 5.1., 5.2., 6.1., 6.2., (6.2.1.) and proofs.}

\section*{References Change}

The following summarizes the changes made in GFIC\_refs\_Minsu.bib file.

\begin{itemize}
\item Arellano, M., Bond, S., 1991: The review of economic studies $\rightarrow$ The Review of Economic Studies
\item Behl, P., Claeskens, G., Dette, H., March 2012: working paper $\rightarrow$ published in Statistica Sinica (2014)
\item Claeskens, G., Croux, C., Jo, 2006: Author name incomplete,  Johan Van Kerckhoven added.
\item DiTraglia, F. J., 2016: volume 192 $\rightarrow$ volume 195
\item Hall, A. R., Peixe, F. P., 2003: Article title and page corrected.
\item Hansen, B. E., 2015: working paper $\rightarrow$ published in Journal of Econometrics (2016)
\item Hong, H., Preston, B., Shum, M., 2003: Article title corrected.
\item Lai, T. L., Small, D. S., Liu, J., 2008: Author name and journal name corrected.
\item Newey, W. K., Smith, R. J., 2004: Article title corrected.
\item Skouras, S., November 2001: working paper $\rightarrow$ published in Journal of Econometrics (2007)
\item Smith, R. J., July 1992. $\rightarrow$ remove July to be consistent with other references.
\end{itemize}


\end{document}
